### 2020-05-27 writeup/proof_examples.tex
prop 4.4

In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  1.32.$$%\frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
Thus the following inequality implies \eqref{solval1}:
\be\label{solval1add}
\begin{split}
&1.32 pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
\end{split}
\ee
In particular, if 
\be\nonumber
\begin{split}
&1.32 pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
\end{split}
\ee
that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
\begin{align*}
\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - (\rho_1-1)(\rho_2-1) \cdot 1.32\frac{pd^2}{\sigma^2}}+ 1\right] \\
& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \frac43\frac{pd^2}{\sigma^2}}+ 1\right] .
\end{align*}

@@

In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
where $\rho:=\rho_1+\rho_2$. 
$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  0.33.$$
Thus the following inequality implies \eqref{solval2}:
\be\label{solval2add}
\begin{split}
&0.33 pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
\end{split}
\ee
There are two cases: if 
\be\nonumber
\begin{split}
&0.33 pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
\end{split}
\ee
then we always have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
\begin{align*}
\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - (\rho_1-1)(\rho_2-1) \cdot 0.33 \frac{pd^2}{\sigma^2}}+ 1\right] \\
& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \frac14\frac{pd^2}{\sigma^2}}+ 1\right] .
\end{align*}
This concludes the proof.

We remark that the constants 1.32 and 0.33 are chosen for all values of $\rho_1/\rho_2$. For a fixed ratio $\rho_1/\rho_2$, one can probably choose much better constants.
\end{proof}

>>>>

In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
Thus the following inequality implies \eqref{solval1}:
\be\label{solval1add}
\begin{split}
&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
\end{split}
\ee
In particular, if 
\be\nonumber
\begin{split}
&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
\end{split}
\ee
that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
\begin{align*}
\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
\end{align*}

@@

In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
Thus the following inequality implies \eqref{solval2}:
\be\label{solval2add}
\begin{split}
&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
\end{split}
\ee
There are two cases: if 
\be\nonumber
\begin{split}
&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
\end{split}
\ee
then we always have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
\begin{align*}
\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
\end{align*}
This concludes the proof.
\end{proof}
